---
title: "Plastic Pollution Around the World"
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    vertical_layout: fill
    theme: sandstone
---

```{r setup, include=FALSE}
library(flexdashboard)
```
-----------------------------------------------------------------------

Blah blah blah Blah blah blah Blah blah blah Blah blah blah Blah blah blah Blah blah blah

-----------------------------------------------------------------------

### Chart A
leaflet of countries with distribution of total plastic counts

  possible chart for each country when selecting, it's a popup (purrr stuff, make ggplot object essentially a list column for each country), think about this

```{r}

```

Row {.tabset .tabset-fade}
-----------------------------------------------------------------------

### Chart B
interactive data table 

  think about adding sparklines (google "r dt sparklines"). have color coded pollutant types.

```{r}

```

### Chart C
bar chart ranking of one country's pollutants

```{r}

```

